Efficient Coalition Formation for Web Services

### 2013-03-03 papers/coalition/coalition.tex
Changes

In this scenario, there are is a community controller by its master web sercice. The community master has some request rate $(R_{master})$ from users. Web services need to join a community to be able to get tasks from a master web service. Each web service comes with different quality of service patameters and a throughput $(T_ws)$. Throughput is the average rate of tasks a web service can perform. Therefore, the master web service is providing tasks with rate of $R_{ws}$ and web services perform tasks with some QoS output metrics and a rate or $T_{ws}$. 
In this setting, we define the value of the coalition as follows:
\begin{equation*}
output(C) = \sum_{ws}{T_{ws}} \times QoS_{ws}
\end{equation*}

\begin{equation*}
v(C) = \left\{ 
  \begin{array}{l l}
    output(C) & \quad \text{if $\sum_{ws}{T_{ws}} \leq R_{master}$}\\
    output(C) \times \frac{R_{master}}{\sum_C{T_{ws}}} & \quad \text{if $\sum_{ws}{T_{ws}} > R_{master}$}
  \end{array} \right.
\end{equation*}

>>>>

In this scenario, there are is a community controller by its master web sercice. The community master has some request rate $(R_{master})$ from users. Web services need to join a community to be able to get tasks from a master web service. Each web service comes with different quality of service patameters and a throughput $(T_ws)$. Throughput is the average rate of tasks a web service can perform. Therefore, the master web service is providing tasks with rate of $R_{ws}$ and web services perform tasks with some QoS output metrics and a rate or $T_{ws}$. 
In this setting, we define the value of the coalition as follows:
\begin{equation*}
output(C) = \sum_{ws}{(T_{ws} \times QoS_{ws})}
\end{equation*}

\begin{equation*}
v(C) = \left\{ 
  \begin{array}{l l}
    output(C) & \quad \text{if $\sum_{ws}{T_{ws}} \leq R_{master}$}\\
    output(C) \times \frac{R_{master}}{\sum_{ws}{T_{ws}}} & \quad \text{if $\sum_{ws}{T_{ws}} > R_{master}$}
  \end{array} \right.
\end{equation*}
